---
title: "Homework2"
author: "Yue Shang"
date: "2/13/2021"
output: word_document
---
1) Enter and run USArrests. What type of information is shown in the data table USArrests?  (Three or four sentences)  
```{r}
library(tidyverse)
library(dplyr)
USArrests
#State, value(double ) of Murder, integer of Assault, integer of UrbanPop, value(double ) of Rape
```
2) Use and show R coding that features a map function to show maximum values for all variables of the USArerests data frame.  Which State has the largest number of Assaults according to the USAressts data frame ?
```{r}
map_dbl(USArrests, max)
#North Carolina has the largest number of Assaults
```

3) Install the nycflights13 package，call the following library, and then enter flights (this will produce the flights data table)
```{r}
library(nycflights13)
flights
```
4) Use and show R code that will indicate how many rows and how many columns the flights data has.  Review and revisit your notes from STAT 412/612.  Describe a tibble (two or three sentences). Now use and show R code that verifies that flights is a tibble  
```{r}
nrow(flights)
ncol(flights)
#tibble() is much lazier than base::data.frame() in terms of transforming the user's input. Character vectors are not coerced to factor. List-columns are expressly anticipated and do not require special tricks. Column names are not modified.tibble() builds columns sequentially. When defining a column, you can refer to columns created earlier in the call. Only columns of length one are recycled.
is_tibble(flights)
```

5) Now Use and show R code (featuring a map function) that will output the type of each column of the flights tibble.  
```{r}
map(flights,typeof)
```  

6)  Use and show R coding that features usage of a map function to find the slope and the intercept of models for the different levels of the Species variable of the iris data frame.  For each model, Sepal.Width predicts Sepal.Length.  
```{r}
abc <- iris %>%
  split(.$Species) %>%
  map(~lm(Sepal.Width  ~  Sepal.Length, data = .))
abc
```

7)  
```{r}
V <- list(12, 22, 27, 31.5, NA, 39, "east")
V
```
7a) Use and show R code to find the length of the list  
```{r}
length(V)
```

7b) Use and show R code that will extract the missing value  
```{r}
V[is.na(V)]
```

7c) Use and show R code that will extract the third object  
```{r}
V[3]
```

7d) Use and show R code that will extract the character string and the minimum number.  
```{r}
V[7] # character string
V[1] #minimum number
```

7e) Use one line of code to show that the seventh object is a character object.  
```{r}
str(V[[7]])
```







